Postural changes mediate children's visual access to social information

### 2018-01-23 writeup-cogsci/cogsci2018_faceOnly.Rmd
fix syntax error in rmd

detectionsByPosture <- dlong %>%
  filter(!is.na(posture)) %>%
  group_by(age.grp, posture, subid,detectorType) %>%
  summarise(face = mean(detection)) %>%
  group_by(age.grp) %%

>>>>

detectionsByPosture <- dlong %>%
  filter(!is.na(posture)) %>%
  group_by(age.grp, posture, subid,detectorType) %>%
  summarise(face = mean(detection)) %>%
  group_by(age.grp)

### 2018-01-23 writeup-cogsci/cogsci2018_faceOnly.tex
fix syntax error in rmd

Our final sample consisted of 36 infants and children, with 8
participants in three age groups: 8 months (6 females), 12 months (7
females), and 16 months (6 females). Participants were recruited from
the surrounding community via state birth records, had no documented
disabilities, and were reported to hear at least 80\% English at home.
Demographics and exclusion rates are given in Table \ref{tab:pop}.

@@

@@

@@

\caption[Proportion face (left) and hand (right) detections as a function of participant's age]{Proportion face (left) and hand (right) detections as a function of participant's age.}\label{fig:detByAge}
\end{figure*}
\end{CodeChunk}

@@

\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
(Intercept) & -4.847 & 0.064 & -75.303 & 0.000 \\ 
  scale(age.at.test) & 0.170 & 0.075 & 2.273 & 0.023 \\ 
  postureprone & -0.513 & 0.042 & -12.326 & 0.000 \\ 
  posturesit & 0.648 & 0.039 & 16.422 & 0.000 \\ 
  posturestand & 1.005 & 0.041 & 24.721 & 0.000 \\ 
  orientationclose & 1.549 & 0.022 & 71.940 & 0.000 \\ 
  orientationfar & 2.258 & 0.022 & 100.357 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Results from GLMM model predicting the presence/absence of a face (MTCNN-Faces) across the entire dataset.} 
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
(Intercept) & -4.847 & 0.064 & -75.303 & 0.000 \\ 
  scale(age.at.test) & 0.170 & 0.075 & 2.273 & 0.023 \\ 
  postureprone & -0.513 & 0.042 & -12.326 & 0.000 \\ 
  posturesit & 0.648 & 0.039 & 16.422 & 0.000 \\ 
  posturestand & 1.005 & 0.041 & 24.721 & 0.000 \\ 
  orientationclose & 1.549 & 0.022 & 71.940 & 0.000 \\ 
  orientationfar & 2.258 & 0.022 & 100.357 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Results from GLMM model prediting the presence/absence of faces (OpenPose-Faces) across the entire dataset.} 
\end{table}

>>>>

Our final sample consisted of 36 infants and children, with 12
participants in three age groups: 8 months (6 females), 12 months (7
females), and 16 months (6 females). Participants were recruited from
the surrounding community via state birth records, had no documented
disabilities, and were reported to hear at least 80\% English at home.
Demographics and exclusion rates are given in Table \ref{tab:pop}.

@@

\caption[Proportion of faces detected by the MTCNN model (left) and the OpenPose model (right panel) as a function of child's age]{Proportion of faces detected by the MTCNN model (left) and the OpenPose model (right panel) as a function of child's age. Larger dots indicate children who had longer playsessions and thus for whom there was more data}\label{fig:detByAge}
\end{figure}
\end{CodeChunk}

@@

{\centering \includegraphics{figs/detByPosOrient-1}

@@

\caption[Proportion face detections as a function of children's posture (top panel) and orientation (bottom panel), binned by the age of the participant]{Proportion face detections as a function of children's posture (top panel) and orientation (bottom panel), binned by the age of the participant.}\label{fig:detByPosOrient}
\end{figure*}
\end{CodeChunk}

@@

\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\
  \hline
(Intercept) & -4.846 & 0.077 & -62.682 & 0.000 \\
  Age & 0.170 & 0.061 & 2.766 & 0.006 \\
  Posture-Prone & -0.513 & 0.036 & -14.045 & 0.000 \\
  Posture-Sit & 0.648 & 0.034 & 18.853 & 0.000 \\
  Posture-Stand & 1.005 & 0.035 & 28.402 & 0.000 \\
  Orient.-Close & 1.549 & 0.021 & 72.757 & 0.000 \\
  Orient.-Far & 2.258 & 0.022 & 101.138 & 0.000 \\
   \hline
\end{tabular}
\caption{Results from GLMM model predicting the presence/absence of a face across the entire dataset (MTCNN detectors).}
\end{table}
